A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-04-22 paper.tex
typos

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
\end{definition}

Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$. The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$. But it also has cohomological degree $-k$. In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.

>>>>

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight $+1$ and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
\end{definition}

Recall that before twisting the bundle $E$ is $\ZZ \times \ZZ/2$-graded.
Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$. The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$. But it also has cohomological degree $-k$. In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.

\begin{rmk}
There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ is such that the twisting supercharge $Q$ is of weight $+1$. 
One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. 
This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be purely even in the new $\ZZ/2$-degree.
\end{rmk}
